Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-14 phd-cs-us.tex
updates

Additionally, \textbf{work experiences at renowned research laboratories}, such as Microsoft Research, can significantly strengthen your
application.  Unfortunately, many good international research places, e.g., VinAI in Vietnam, remain relatively unknown to most universities in the US. So you should explicit say something about them in your statement.

@@

\begin{wrapfigure}{r}{0.45\textwidth}
    \vspace{-0.3in}
      \begin{center}
        \includegraphics[width=0.45\textwidth]{c6.png}
      \end{center}
    \vspace{-0.4in}
    \end{wrapfigure}
Many students have letters written by the applicants themselves and signed by their professors. These have little
values (we can easily recognize them) and will consider them weakness.
Similarly, many professors write very generic letters for students (a common example is that the students didn't do any
research or make any impression for the professor to write about). These letters are also not useful and considered weak.

@@

\subsection{Tenured or tenure-track faculty? Who do you choose?} 
The short answer is that tenured-track faculty (e.g., assistant professors) are more likely to be young and very active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. The downside is that they may not have as much experience in managing students and may not have as much funding as tenured faculty.
Tenured faculty (e.g., associate and full profs.) are more likely to be older, more well-known, and have more experience in managing students.  However, they might not push you as hard (they don't have to, they already got tenured) and expect you to figure things out yourself (so you need to be very independent).  Some tenured faculty are also no longer active in research, e.g., they are more involved in administrative duties.

@@

# ** Self-funded
# - Some PhD students are funded through their company
#   - The students work full time for the company and do their PhD part-time
#   - Typically will take longer (because you have to work full time) and require some serious committement from the students

>>>>

Additionally, \textbf{work experiences at renown research laboratories}, such as Microsoft Research, can significantly strengthen your
application.  Unfortunately, many good international research places, e.g., VinAI in Vietnam, remain relatively unknown to most universities in the US. So you should explicit say something about them in your statement.

@@

\begin{wrapfigure}{r}{0.47\textwidth}
    \vspace{-0.35in}
      \begin{center}
        \includegraphics[width=0.47\textwidth]{c6.png}
      \end{center}
    \vspace{-0.4in}
    \end{wrapfigure}
Many students have letters written by the applicants themselves and signed by their professors. These have little
values (we can easily recognize them) and will consider them weakness.
Similarly, many professors write very generic letters for students (a common example is that the students didn't do any
research or make any impression for the professor to write about). These letters are also not useful and considered weak.

@@

\subsection{Tenured or tenure-track faculty? Who do you choose?}

\begin{wrapfigure}{r}{0.45\textwidth}
    \vspace{-0.35in}
      \begin{center}
        \includegraphics[width=0.45\textwidth]{c8.png}
      \end{center}
    \vspace{-0.3in}
    \end{wrapfigure}The short answer is that tenured-track/untenured faculty (e.g., assistant professors) are more likely to be young and very active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. The downside is that they may not have as much experience in managing students and may not have as much funding as tenured faculty.
Tenured faculty (e.g., associate and full profs.) are more likely to be older, well-known, and have more experience in managing students.  However, they might not push you as hard (they don't have to, they already got tenure) and expect you to figure things out yourself (so you need to be very independent).  Some tenured faculty are also no longer active in research, e.g., they are more involved in administrative duties.

@@

# ** Self-funded
# - Some PhD students are funded through their company
#   - The students work full time for the company and do their PhD part-time
#   - Typically will take longer (because you have to work full time) and require some serious commitment from the students
